NGO analysis

### 2022-08-02 Dashboard/NGO Analysis dashboard v006.Rmd

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed and avoiding
# catastrophic dashboard errors if they're not available
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

>>>>

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed and avoiding
# catastrophic dashboard errors if they're not available
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools, purrr
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

### 2022-08-02 Dashboard/report.Rmd

exceldata <- widen_excel(excel_test)

# NGO title ==================================================================

NGO <- excel_test |>
  # Turning the needed column into a list
  pull(firm) |>
  # discarding all NAs in case the name is somewhere
  purrr::discard(is.na) |>
  # choosing the first available name
  first()

@@

# Creating general warning
general_warning <- if (
  datatest == TRUE ||
    sum(!is.na(htmldata$arsresultat)) == 0 ||
    sum(!is.na(htmldata$sum_egenkapital_og_gjeld)) == 0 ||
    (sum(!is.na(htmldata$lederlonn)) == 0 &&
      sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) ||
    excel_zero_check("Revenue") == 0 ||
    excel_zero_check("Expenses") == 0
) {
  "## Note:"
} else {
  ""
}
```

@@

```{r functions_reliant}
## scale maximum--------------------------------------------------------------
# Function to create the maximum value for revenue and expenses plots
maximum <- if (datatest == TRUE) {
  NA
} else {
  excel_test |>
    # removing the firm and sub-category columns
    select(-firm, -sub_category) |>
    # filtering to retain only revenue and expenses entries
    filter(category == "Revenue" | category == "Expenses") |>
    # grouping and summarising to calculate maximum value
    group_by(year, category) |>
    summarise(
      sum = sum(value, na.rm = TRUE)
    ) |>
    # Creating list of sums
    pull() |>
    # selecting the highest value
    max()
}

@@

```{r revenue_expenses_plot_both, fig.asp=1, out.width="50%", fig.cap="Revenue and Expenses", fig.subcap=c("Based on the category \`Revenue' in the Excel sheet.", "Based on the category \`Expenses' in the Excel sheet.")}

# Printing the plots if the data are OK
if (is.ggplot(revenue_plot) && is.ggplot(expenses_plot)) {
  revenue_plot
}

>>>>

exceldata <- widen_excel(excel_test)
```

```{r ngo_title}
# NGO title ==================================================================
NGO <- excel_test |>
  # Turning the needed column into a list
  pull(firm) |>
  # discarding all NAs in case the name is somewhere
  purrr::discard(is.na) |>
  # choosing the first available name
  first()

@@

## Creating general warning-----------------------------------------------------
general_warning <- if (
  datatest == TRUE ||
    sum(!is.na(htmldata$arsresultat)) == 0 ||
    sum(!is.na(htmldata$sum_egenkapital_og_gjeld)) == 0 ||
    (sum(!is.na(htmldata$lederlonn)) == 0 &&
      sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) ||
    excel_zero_check("Revenue") == 0 ||
    excel_zero_check("Expenses") == 0
) {
  "## Note:"
} else {
  ""
}
```

@@

```{r functions_reliant}
## scale maximum--------------------------------------------------------------
# Function to create the maximum value for revenue and expenses plots
# Testing, because this function cannot rely on the reactive chain to stop
maximum <- if (datatest == TRUE) {
  NA
} else {
  excel_test |>
    # removing the firm and sub-category columns
    select(-firm, -sub_category) |>
    # filtering to retain only revenue and expenses entries
    filter(category == "Revenue" | category == "Expenses") |>
    # grouping and summarising to calculate maximum value
    group_by(year, category) |>
    summarise(
      sum = sum(value, na.rm = TRUE)
    ) |>
    # Creating list of sums
    pull() |>
    # selecting the highest value
    max()
}

@@

```{r revenue_expenses_plot_both, fig.asp=1, out.width="50%", fig.cap="Revenue and Expenses", fig.subcap=c("Based on the category \`Revenue' in the Excel sheet.", "Based on the category \`Expenses' in the Excel sheet.")}
# Printing the plots if the data are OK
if (is.ggplot(revenue_plot) && is.ggplot(expenses_plot)) {
  revenue_plot
}
